Backpropagating Gravitational wave events

### 2022-03-17 src/ms.tex
typo fix

\begin{figure*}
\includegraphics[width=0.98\textwidth]{static/GW150914_corner.pdf}
\caption{The posterior for GW150914 in both the progenitor parameter space and hyper-parameter space.
$M_1$ and $M_2$ are the progenitors' masses. $\log{t_{orb}}, e, \log{Z}$ are the progenitor binary's log orbital period, eccentricity and log metallicity at ZAMS.
$\alpha$ is the common envelope efficiency.
$f_{\rm acc}$ is the fraction of mass accreted during stable mass transfer.
$q_{\rm crit 3,4}$ are the cirtical mass during \kw{Katie fill in},
$\sigma$ is the mean magnitude of the Maxwellian distribution characterizing natal kick strength.
}
\label{fig:GW150914_posterior}
\end{figure*}

>>>>

\begin{figure*}
\includegraphics[width=0.98\textwidth]{static/GW150914_corner.pdf}
\caption{The posterior for GW150914 in both the progenitor parameter space and hyper-parameter space.
$M_1$ and $M_2$ are the progenitors' masses. $\log{t_{orb}}, e, \log{Z}$ are the progenitor binary's log orbital period, eccentricity and log metallicity at ZAMS.
$\alpha$ is the common envelope efficiency.
$f_{\rm acc}$ is the fraction of mass accreted during stable mass transfer.
$q_{\rm crit 3,4}$ are the critical mass during \kw{Katie fill in},
$\sigma$ is the mean magnitude of the Maxwellian distribution characterizing natal kick strength.
}
\label{fig:GW150914_posterior}
\end{figure*}
